# UNEMPLOYMENT IN INDIA

1.  Uploading the data

```{r}
Unemployment1<-read.csv("C:/Users/parul/Desktop/Congno Rise Internship/Unemployment in India.csv")
```

```{r}
Unemployment1
```

2.  Changing the column names for simplicity

```{r}
colnames(Unemployment1)<-c("Region","Date","Frequency","Estimated_Unemp_Rate","Estimated_Emp_Rate","Estimated_Labour_Rate","Areas")
```

```{r}
names(Unemployment1)
```

3.  Installing the required packages

```{r}
library("ggplot2")
```

```{r}
library("plotly")
```

```{r}
library("corrplot")
```

4.  Getting the summary for Estimated Unemployment Rate

```{r}
summary(Unemployment1$Estimated_Unemp_Rate)
```

5.  Summary for Estimated Employment Rate

```{r}
summary(Unemployment1$Estimated_Emp_Rate)
```

6.  Summary for Estimated Labor Participation

```{r}
summary(Unemployment1$Estimated_Labour_Rate)
```

7.  Regression of Unemployment Rate on Employed

```{r}
ggplot(Unemployment1,aes(x=Estimated_Emp_Rate,y=Estimated_Unemp_Rate))+
  geom_point(aes(color=Region),alpha=0.6)+
  geom_smooth(method="lm",formula = y~x,se=FALSE,color="blue")+
  labs(title="Regression of Unemployment Rate on Employed",x="Employed",y="Unemployment Rate")
```

THIS SHOWS THAT AS THE NEGATIVE RELATIONSHIP BETWEEN UNEMPLOYMENT & EMPLOYMENT RATES

8.  Bar plot for the Mean Estimated Unemployment Rate by Region

```{r}
UE_grouped1<-aggregate(Estimated_Unemp_Rate~Region,data = Unemployment1,FUN = mean)
```

```{r}
ggplot(UE_grouped1,aes(x=Region,y=Estimated_Unemp_Rate))+
  geom_bar(stat = "identity",fill="skyblue")+
  theme(axis.text.x = element_text(angle = 90,vjust = 0.5,hjust = 1))+
  labs(title = "Mean Estimated Unemployment Rate by Region",
       x = "Region", y = "Mean Estimated Unemployment Rate")
```

MEAN ESTIMATED UNEMPLOYMENT RATE IN UTTAR PRADESH IS HIGH FOLLOWED BY HARYANA

9.  Box Plot for showing the effect of regions on Unemployment Rates

```{r}
ggplot(Unemployment1)+
  geom_boxplot(mapping = aes(x=Region,y=Estimated_Unemp_Rate,fill=Region),color="darkgrey")+
  theme(axis.text.x = element_text(angle = 90,vjust = 0.5,hjust = 1))+
  labs(title = "Effect of Regions on Unemployment Rate",x="Region",y="Unemployment Rate")
```

10. Correlation between Estimated Unemployment rate, estimated employment rate and labor participation.

```{r}
Unemployment2<- Unemployment1[,c(4,5,6)]
```

```{r}
Unemployment2
```

```{r}
cor2<-cor(Unemployment2)
```

```{r}
cor2
```

11. Plotting a Corr plot for showing the correlation between the three numerical variables

```{r}
corrplot(cor2,method="circle",tl.srt=45,type="upper",tl.cex = 0.5,tl.col = "black")
```

12. Pie Chart for the distribution of estimated unemployment rate through regions

```{r}
UE_G2 <- aggregate(Estimated_Unemp_Rate ~ Region, data = Unemployment1, FUN = sum)
```

```{r}
ggplot(UE_G2, aes(x = "", y = Estimated_Unemp_Rate, fill = Region)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  labs(title = "Distribution of Estimated Unemployment Rate by Region") +
  theme_void() +
  theme(legend.position = "right") 
```

13. Histogram of estimated unemployment rate by areas

```{r}
ggplot(Unemployment1,aes(x=Estimated_Unemp_Rate,fill=Areas))+
  geom_histogram(binwidth = 1,color="darkgrey",alpha=0.7)+
  labs(title = "Histogram of Estimated Unemployment Rate",x="Estimated Unemployment Rate",y="Count")+
  theme_grey()
```

14. Anova to test the differences in unemployment rates by regions

```{r}
anova_model1<-aov(Estimated_Unemp_Rate~Region,data=Unemployment1)
summary(anova_model1)
```

15. Histogram for the Estimated Employed Labor

```{r}
ggplot(Unemployment1,aes(Estimated_Emp_Rate))+
  geom_histogram(bins = 30,fill="#03322A",alpha=0.6)+
  labs(title="Histogram of Estimated Employed",x="Employed",y="Count")
```

17. Histogram for Estimated labor Rate

```{r}
ggplot(Unemployment1,aes(Estimated_Labour_Rate))+
  geom_histogram(bins = 30,fill="#013E62",alpha=0.6)+
  labs(title = "Histogram of Labour Participation",x="Labour Participation Rate",y="Count")
```

18. Histogram for Estimated Unemployment Rate

```{r}
{r}
ggplot(Unemployment1,aes(x=Estimated_Unemp_Rate))+
  geom_histogram(bins=30,fill="sienna",alpha=0.6)+
  labs(title = "Histogram of Estimated Unemployment Rate",x="Estimated Unemployment Rate",y="Count")
```

19. Line graph showing unemployment rates over states

```{r}
ggplot(Unemployment1,aes(x=Region,y=Estimated_Unemp_Rate,group=Areas,color=Areas))+
  geom_line()+
  labs(title = "Unemployment Rate over States",x="Region",y="Unemployment Rate")+
  theme(axis.text.x = element_text(angle = 90,vjust = 0.5,hjust = 1))
```

20. Pie Chart for showing Unemployment Rates according to the Areas

```{r}
plot_ly(Unemployment1,labels= ~Areas,type="pie",hole=0.5,textposition="inside")
```
